---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# betterBudgets

<!-- badges: start -->
<!-- badges: end -->

The goal of the betterBudgets package is to help users better manage their budgets. It takes the user's income (of any currency) as input and then calculates how much they should spend on healthcare, housing, savings, and so on. It also provides them with personalized recommendations for specific budgets. There is, for example, a function that provides housing recommendations based on the state, annual income, and the desired type of housing.

## Installation

You can install the development version of betterBudgets from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("Adv-R-Programming/final-project-better-budgets")
```

If you get a warning that says that "qpdf is needed," install qpdf.

## Example

This is a basic example which shows you how to use the individual budgeting functions:

```{r example}
library(betterBudgets)
# calling transportation_budget for a user with a monthly income of $8000, requesting additional saving tips, and saving recommendations. To request saving recommendations the user must also provide their monthly distance, along with their car consumption, and the cost of fuel.
transportation_budget(8000, tip = TRUE, rec = TRUE, dist = 800, consump = 25, cpg = 3 )

# calling food_budget for a user with a monthly income of $8000. Returns the recommended food spending for an individual with a monthly income of $8000, along with food saving tips, and splitting the food budget further into two categories: groceries and takeout
food_budget(8000, tip = TRUE, food_split = TRUE)

# calling healthcare_budget for a user with a monthly income of $8000. Returns the recommended healthcare spending for an individual with a monthly income of $8000
healthcare_budget(8000)

# calling housing_budget for a user with a monthly income of $8000. Returns the recommended housing spending for an individual with a monthly income of $8000 along with saving tips
housing_budget(8000, tip = TRUE)

# calling other_budget for a user with a monthly income of $8000. Returns the recommended other spending for an individual with a monthly income of $8000
other_budget(8000)

# calling savings_budget for a user with a monthly income of $8000. Returns the recommended savings for an individual with a monthly income of $8000
savings_budget(8000)

```

We also have an interactive monthly budget function that combines all the individual budget functions and creates a monthly budget for the user. 

```{r}
# returns a monthly budget for an income of $8000. Additionally, the users can specify which categories are most important to them by rating each category from 1-6. The percent of income for each category will vary depending on the level of importance attributed to it. The results will then be displayed in a bar graph
monthly_budget_more (8000, interactive = FALSE )

```

# Overview

The main components of this package include functions that calculate a recommended or self-selected budget for the following categories: housing, healthcare, food, transportation, savings, and other. In addition to these functions, there are also functions that provide housing recommendations based on location and income, as well as a function that provides tips on how to save money. The individual budgeting functions are smaller, and are used together in the helper function: monthly_budget_more(). This function along with a function that takes user input (interact()), are used in the main function do_both(), and allows the user input their income, rate the importance of the different budget components to set their percentages (or use the recommended budget percentages), and run calculations for each of the budget components to output their spending allotment for each budget component. Please see the vignette “Interactive Monthly Budget” to get a more detailed description of the functionality and uses of the interact(), monthly_budget_more(), and do_both() functions. The “Advanced Functions” vignette will give you a more detailed description of the advanced functionalities of the transportation_budget() and food_budget() functions.
