---
title: "betterBudgets"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{betterBudgets}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(betterBudgets)
```

## Introduction 

This package is meant to help users budget better easily. It provides functions to compute monthly income, and then use that to create different components of the users monthly budget. This will include functions to calculate healthcare, food, and savings budgets, among others.

## Functions

The package includes the following functions:

  - `user_income()`
  
    + `user_income()` enables users to input their annual income which is 
    converted to monthly income. The other functions like percentage of income 
    that should be spent on healthcare can then be built on this function. 
  
  - `healthcare_budget()`
  
    + `healthcare_budget()` enables users to calculate how much income they should
    set aside for healthcare, depending on their monthly income
  
  - `housing_budget()`
  
    + `housing_budget()` enables users to calculate how much income they should
    set aside for housing, depending on their monthly income
  
  - `savings_budget()`
  
    + `savings_budget()` enables users to calculate how much income they should
    set aside for their savings, depending on their monthly income
  
  - `food_budget()`
  
    + `food_budget()` enables users to calculate how much income they should
    set aside for food, depending on their monthly income
  
  - `transportation_budget()`
  
    + `transportation_budget()` enables users to calculate how much income they
    should set aside for transportation, depending on their monthly income
  
  - `other_budget()`
  
    + `other_budget()` enables users to calculate how much income they should
    set aside for miscellaneous purposes, depending on their monthly income
    
  - `monthly_budget_more()`
  
    + `monthly_budget_more()` enables users to get a summary table of how much they
    should set aside for each major budget area, depending on how they rate the
    different and their monthly income
  
  - `housing_rec()` 
    + `housing_rec()` enables users to get a summary table of housing
    recommendations:
    
      * if they input a state abbreviation, they will get a recommendation for
      how much they should earn annually to own a home in that state
      
      * if they input the kind of home they want to own, which can be one of 
      "Rent", "Conventional", "Contemporary", or "Multi-Storey Home", then they
      get a recommendation for how much they should earn annually to own that kind
      of home
      
      * if they input their annual income, they get a recommendation for the kind
      of home they can own with that income

## Examples 

To use the `user_income()`, simply enter the user's yearly income as a numeric value. 

```{r}
# Calculating monthly income for a yearly income of 100000

income <- 100000
monthly_income <- user_income(100000)
monthly_income 

```

You can use `food_budget` to compute the recommended value to set aside for food for an annual income of $70,000

```{r}
food_budget(70000)
```


You can use `other_budget()` to compute the recommended values to set aside
for miscellaneous purposes for different incomes.

```{r}
other_budget(10000, 202020, 123456)
```

You can use `housing_rec()` to get housing recommendations for:

  - a person living in New York
  
  - a person living in California
  
  - a person who earns $100,000 annually
  
  - a person who wants to rent a house
  
  - a person who earns $60,000 annually
  
```{r}
housing_rec("NY", "CA", "$100,000", "Rent", 60000)
```









