---
title: "Interactive Monthly Budget"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Interactive Monthly Budget}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(betterBudgets)
```


## Introduction

The `monthly_budget_more()` function allows users to get a summary table and bar 
plot of monetary allocations for different budget areas, including food, 
healthcare, transportation, housing, savings, and miscellaneous. 

The default setting of the function, which has the argument `interactive` set to
`FALSE` provides suggestions based on nationally recommended values for different
budget areas. However, setting `interactive` to `TRUE` allows users to rate how
important these different areas are for them, and then computes budget allocations
accordingly.

The `do_both()` function is an extension of `monthly_budget_more()`, and allows
you to have an interactive interface to enter your income.

## Examples

You can get a summary table and visualization for budget allocations for an 
annual income of $100,000 like se:

```{r}
my_budget <- monthly_budget_more(100000)

# access the summary table
my_budget$budget

# access the visualization
my_budget$bar_plot
```


You can also modify different parameters of the visualization by inputting
arguments that are fed into the `layer()` function in the `ggplot2` package.

For example, to get a bar plot of orchid colored-fill, simply input 
`fill = "orchid` like so:

```{r}
my_budget <- monthly_budget_more(100000, fill = "orchid")

# access the summary table
my_budget$budget

# access the visualization
my_budget$bar_plot
```


You can also rate how important the different budget areas are for you by setting
the `interactive` parameter to `TRUE`

```{r}
# my_budget <- monthly_budget_more(100000, interactive = TRUE, fill = "orchid")
```





